No Massive Companion to the Low-Frequency, Coherent Radio-Emitting M~Dwarf GJ\,1151

### 2019-08-27 paper/ms.tex
title caps
plotone

\title{No Massive Companion to the low-frequency, coherent radio-emitting M~Dwarf GJ\,1151}

@@

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{comparison_validation.pdf}

@@

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_samples_trend.png}

\caption{\label{jokermodel1151}
\textit{The Joker} posterior samples for GJ\,1151.
}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{cornerplot_km_trend.png}

>>>>

\title{No Massive Companion to the Low-Frequency, Coherent Radio-Emitting M~Dwarf GJ\,1151}

@@

\begin{figure}
\plotone{comparison_validation.pdf}

@@

\begin{figure}
\plotone{gj1151b_samples_trend.png}
\caption{\label{jokermodel1151}
\textit{The Joker} posterior samples for GJ\,1151.
}
\end{figure}

\begin{figure}
\plotone{cornerplot_km_trend.png}
